\pkg{partykit}: A Modular Toolkit for Recursive Partytioning in \proglang{R}

### 2014-03-25 pkg/partykit/inst/mloss/mloss2.Rnw
some more references
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@549 255f4249-2263-4417-b1ea-8498779e27a7

%% header declarations
\author{Torsten Hothorn \\ \addr{Universit\"at Z\"urich} \\ \addr{E-mail: Torsten.Hothorn@R-project.org} \AND
        Achim Zeileis \\ \addr{Universit\"at Innsbruck} \\ \addr{E-mail: Achim.Zeileis@R-project.org}}
\title{\pkg{partykit}: A Modular Toolkit for Recursive Partytioning in \proglang{R}}
\editor{(submission for MLOSS track)}

@@

@@

\section{Internal Structure}

>>>>

%% header declarations
\author{Torsten Hothorn \\ \addr{Universit\"at Z\"urich} \\ \addr{E-mail: Torsten.Hothorn@R-project.org} \AND
        Achim Zeileis \\ \addr{Universit\"at Innsbruck} \\ \addr{E-mail: Achim.Zeileis@R-project.org}}
\title{\pkg{partykit}: A Modular Toolkit for Recursive Partytioning in \proglang{R}}
\editor{(submission for MLOSS track, related to JMLR-07-240-1 that was handled by Cheng Soon Ong)}

@@

\fct{rpart} from \pkg{rpart} \citep{rpart}
CART \citep{Breiman+Friedman+Olshen:1984}

C4.5 \citep{Quinlan:1993}
\fct{J48} from \pkg{RWeka} \citep{RWeka} interfacing \pkg{Weka} \citep{Witten+Frank:2005}

QUEST \citep{Loh+Shih:1997}

CTree \citep{Hothorn+Hornik+Zeileis:2006}
MOB \citep{Zeileis+Hothorn+Hornik:2008}

 among many others
\citep[see][for a recent overview]{Loh:2014}. Reflecting the heterogeneity
of conceptual algorithms, a wide range of computational implementations
in various software systems emerged: Typically the original authors of an
algorithms also provide accompanying software but many software systems,
e.g., including  or \proglang{R} \citep{R},
also provide collections of various types of trees.
Within \proglang{R} the list of prominent packages includes

@@

\section{Developer Infrastructure}
